{\bf Practical Concurrency Testing} \\ \normalsize \vspace{1em} \begin{tabular}{c} {\em or, How I Learned to Stop Worrying and Love the Exponential Explosion} \end{tabular}

### 2018-03-01 thesis/thesis.tex
landslide lecture - copy 2017 2018
quotes

% some useful packages
\usepackage{fullpage}
\usepackage{graphicx}
\usepackage{amsmath}
\usepackage{amssymb}
\usepackage[numbers,sort]{natbib}
\usepackage[backref,pageanchor=true,plainpages=false, pdfpagelabels, bookmarks,bookmarksnumbered,
%pdfborder=0 0 0,  %removes outlines around hyper links in online display
]{hyperref}
\usepackage{subfigure}
\usepackage{xspace}

@@

\chapter{Quicksand}
%\inspirationalquote{
%\begin{tabular}{p{0.55\textwidth}}
%There are awful, horrible things in this world; I know that now.
%But there are a lot of things worth protecting, too.
%\end{tabular}}
%{Kaname Madoka, Mahou Shoujo Madoka{\raisebox{0.1em}{$\scriptstyle \bigstar$}}Magica}
\inspirationalquote{Always, somewhere, someone is fighting for you.
As long as you remember her, you are not alone.}
{Mahou Shoujo Madoka{\raisebox{0.1em}{$\scriptstyle \bigstar$}}Magica}

@@

@@

\chapter{Conclusion}
\inspirationalquote{
	\begin{tabular}{p{0.84\textwidth}}
	"If you are a god, Zeus, as the stories claim, then why did you create evolution?
	Why did you make a world that can only grow through cruelty and pain?"
	\\
	For a moment\inspirationalhyphen{}surely this meant death was near\inspirationalhyphen{}she thought she heard him answer:
	"My child, I was shaped by the gods that came before me, as you were shaped by me.
	The choice I had was between creation and oblivion, life and death.
	And I chose life, because any life is better than no life,
	because as long as there is life, there is hope\inspirationalhyphen{}if not for us, then for some generation to come."
	\\
	"Then how are you a god, if you can offer so little?" she whispered, feeling death creep closer.
	\\
	"I am a god because I take upon myself the burden of creation," the statue replied.
	\\
	"Then we are all gods," Alexandra said, and pushed the button.
	\end{tabular}}
{Galatea, The Talos Principle}

>>>>

% some useful packages
\usepackage{fullpage}
\usepackage{graphicx}
\usepackage{amsmath}
\usepackage{amssymb}
\usepackage[numbers,sort]{natbib}
\usepackage[backref,pageanchor=true,plainpages=false, pdfpagelabels, bookmarks,bookmarksnumbered,
%pdfborder=0 0 0,  %removes outlines around hyper links in online display
]{hyperref}
\usepackage{subfigure}
\usepackage{xspace}
\usepackage[linesnumbered,ruled]{algorithm2e}
\usepackage{algpseudocode}

@@

\chapter{Quicksand}
\inspirationalquote{
% original
% {\footnotesize 嫌な事も悲しい事もあったけど、守りたい物だって沢山この世界にはあったから…} \\
% trans. slightly paraphrased from crunchyroll subtitle; removed "..."s, added past tense for あった
There were awful, sad things in this world.
But there were a lot of things worth protecting, too.
}
{Kaname Madoka, Mahou Shoujo Madoka{\raisebox{0.1em}{$\scriptstyle \bigstar$}}Magica}
%\inspirationalquote{Always, somewhere, someone is fighting for you.
%As long as you remember her, you are not alone.}
%{Mahou Shoujo Madoka{\raisebox{0.1em}{$\scriptstyle \bigstar$}}Magica}

@@

\chapter{Transactions}
%\inspirationalquote{

@@

\chapter{Conclusion}
\inspirationalquote{
	\begin{tabular}{p{0.84\textwidth}}
	"If you are a god, Zeus, as the stories claim, then why did you create evolution?
	Why did you make a world that can only grow through cruelty and pain?"
	\\
	For a moment\inspirationalhyphen{}surely this meant death was near\inspirationalhyphen{}she thought she heard him answer:
	"My child, I was shaped by the gods that came before me, as you were shaped by me.
	The choice I had was between creation and oblivion, life and death.
	And I chose life, because any life is better than no life,
	because as long as there is life, there is hope\inspirationalhyphen{}if not for us, then for some generation to come."
	\\
	"Then how are you a god, if you can offer so little?" she whispered, feeling death creep closer.
	\\
	"I am a god because I take upon myself the burden of creation," the statue replied.
	\\
	"Then we are all gods," Alexandra said, and pushed the button.
	\end{tabular}}
%{Galatea, The Talos Principle}
{The Talos Principle}
